Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-12-04 paper/paper.tex
rainbow stuff (response to reviewer)

>>>>

\paragraph*{Self-training may introduce bias. How to alleviate it ?}
As pointed out by one of the reviewers, self-training may introduce bias due to information shortage caused by the absence of external stimulus (task).
 way to solve this issue is to use importance sampling as was done in ~\citep{schaul2015} and ~\citep{hessel2017}, to replay more often state-transitions from which there is more to learn. New transitions are inserted into the replay buffer with maximum priority, providing a bias towards recent transitions. Such an insertion bias would help counter-balance the bias introduced by the information shortage caused by the absence of external stimulus (task). Also, ~\citep{hessel2017} noticed that such prioritized replay reduces the data-complexity and the agent can start learning much sooner than conventionally.
